Supporting Information : Asymmetric tail-association in extreme climatic events affects population-extinction risk

### 2019-10-11 SuppMat.Rmd
extreme and moderate results combined in single plot

@@

  plot(ss$d,ss$risk_mleft,xlim=range(ss$d),ylim=c(0,1),type="b",col="red",
       #panel.first = grid(),
       xlab="d",ylab="Extinction risk",cex.lab=2,cex.axis=1.5)
  lines(ss$d,ss$risk_mright,type="b",col="blue")
  #legend("bottomleft", c("noise : left","noise : right"), lty=c(1,1), pch=c(1,1), 
  #       col=c('red', 'blue'), horiz=T, bty='n', cex=1.2)
  mtext(paste0("r = ", round(rlist[i],5)),cex=1.2)
}
par(op)
dev.off()
```

@@

lines(ricker_extrisk_d0$r,ricker_extrisk_d0$risk_mright_d0,col="blue",type="b",ylim=c(0,1),pch=1)
arrows(x0=ricker_extrisk_d0$r,y0=ricker_extrisk_d0$CI0.025mright,
       x1=ricker_extrisk_d0$r,y1=ricker_extrisk_d0$CI0.975mright,angle=90,length=0.1,col="blue",code=3)
legend("topleft", legend=c("Ricker"), horiz=F, bty='n',cex=1.8)  
mtext(paste0("K = ",K),side = 3, line=-16, adj=0.95, cex=1.8, col="black")
legend("bottomright",legend=bquote(sigma==.(scl)), horiz=F,bty='n',cex=1.8)
#legend("bottomright", legend=c("Ricker",paste0("K = ",K)), horiz=F, bty='n',cex=1.8)
par(op)
dev.off()
```

@@

  plot(ss$d,ss$risk_mleft,xlim=range(ss$d),ylim=c(0,1),type="b",col="red",
       #panel.first = grid(),
       xlab="d",ylab="Extinction risk",cex.lab=2,cex.axis=1.5)
  lines(ss$d,ss$risk_mright,type="b",col="blue")
  #legend("bottomleft", c("noise : left","noise : right"), lty=c(1,1), pch=c(1,1), 
  #       col=c('red', 'blue'), horiz=T, bty='n', cex=1.2)
  mtext(paste0("r = ", round(rlist[i],5)),cex=1.2)
}
par(op)
dev.off()
```

@@

lines(hassell_extrisk_d0$r,hassell_extrisk_d0$risk_mright_d0,col="blue",type="b",ylim=c(0,1),pch=1)
arrows(x0=hassell_extrisk_d0$r,y0=hassell_extrisk_d0$CI0.025mright,
       x1=hassell_extrisk_d0$r,y1=hassell_extrisk_d0$CI0.975mright,angle=90,length=0.1,col="blue",code=3)
legend("topleft", legend=c("Hassell"), horiz=F, bty='n',cex=1.8)  
mtext(paste0("a = ",a,", b = ",b),side = 3, line=-16, adj=0.9, cex=1.8, col="black")
legend("bottomright",legend=bquote(sigma==.(scl)), horiz=F,bty='n',cex=1.8)
#legend("bottomright", c("Hassell",paste0("a = ",a," ,b = ",b),paste0("sd =",scl)), horiz=F, bty='n',cex=1.8)
par(op)
dev.off()
```

@@

  plot(ss$d,ss$risk_mleft,xlim=range(ss$d),ylim=c(0,1),type="b",col="red",
       xlab="d",ylab="Extinction risk",cex.lab=2,cex.axis=1.5)
  lines(ss$d,ss$risk_mright,type="b",col="blue")
  mtext(paste0("r = ", round(rlist[i],5)),cex=1.2)
}
par(op)
dev.off()
```

@@

lines(msmith_extrisk_d0$r,msmith_extrisk_d0$risk_mright_d0,col="blue",type="b",pch=1)
arrows(x0=msmith_extrisk_d0$r,y0=msmith_extrisk_d0$CI0.025mright,x1=msmith_extrisk_d0$r,
       y1=msmith_extrisk_d0$CI0.975mright,angle=90,length=0.1,col="blue",code=3)
legend("topleft", legend=c("Maynard Smith"), horiz=F, bty='n',cex=1.8)  
mtext(paste0("a = ",a,", b = ",b),side = 3, line=-16, adj=0.9, cex=1.8, col="black")
legend("bottomright",legend=bquote(sigma==.(scl)), horiz=F,bty='n',cex=1.8)
par(op)
dev.off()
```

@@

  plot(ss$d,ss$risk_mleft,xlim=range(ss$d),ylim=c(0,1),type="b",col="red",
       xlab="d",ylab="Extinction risk",cex.lab=2,cex.axis=1.5)
  lines(ss$d,ss$risk_mright,type="b",col="blue")
  mtext(paste0("r = ", round(rlist[i],5)),cex=1.2)
}
par(op)
dev.off()
```

@@

lines(pennycuick_extrisk_d0$r,pennycuick_extrisk_d0$risk_mright_d0,col="blue",type="b",ylim=c(0,1),pch=1)
arrows(x0=pennycuick_extrisk_d0$r,y0=pennycuick_extrisk_d0$CI0.025mright,x1=pennycuick_extrisk_d0$r,
       y1=pennycuick_extrisk_d0$CI0.975mright,angle=90,length=0.1,col="blue",code=3)
legend("topleft", legend=c("Pennycuick"), horiz=F, bty='n',cex=1.8)  
mtext(paste0("a = ",a,", b = ",b),side = 3, line=-16, adj=0.9, cex=1.8, col="black")
legend("bottomright",legend=bquote(sigma==.(scl)), horiz=F,bty='n',cex=1.8)
#legend("bottomright", c("Pennycuick",paste0("a = ",a," ,b = ",b),paste0("sd =",scl)), horiz=F, bty='n',cex=1.8)
par(op)
dev.off()
```

@@

  plot(ss$d,ss$risk_mleft,xlim=range(ss$d),ylim=c(0,1),type="b",col="red",
       xlab="d",ylab="Extinction risk",cex.lab=2,cex.axis=1.5)
  lines(ss$d,ss$risk_mright,type="b",col="blue")
  mtext(paste0("r = ", round(rlist[i],5)),cex=1.2)
}
par(op)
dev.off()
```

@@

lines(verhulst_extrisk_d0$r,verhulst_extrisk_d0$risk_mright_d0,col="blue",type="b",pch=1)
arrows(x0=verhulst_extrisk_d0$r,y0=verhulst_extrisk_d0$CI0.025mright,
       x1=verhulst_extrisk_d0$r,y1=verhulst_extrisk_d0$CI0.975mright,angle=90,length=0.1,col="blue",code=3)
legend("topleft", legend=c("Verhulst"), horiz=F, bty='n',cex=1.8)  
mtext(paste0("K = ",K),side = 3, line=-16, adj=0.9, cex=1.8, col="black")
legend("bottomright",legend=bquote(sigma==.(scl)), horiz=F,bty='n',cex=1.8)
#legend("bottomright", c("Verhulst",paste0("K =1, sd =",scl)), horiz=F, bty='n',cex=1.8)
par(op)
dev.off()
```

@@

  plot(ss$d,ss$risk_mleft,xlim=range(ss$d),ylim=c(0,1),type="b",col="red",
       xlab="d",ylab="Extinction risk",cex.lab=2,cex.axis=1.5)
  lines(ss$d,ss$risk_mright,type="b",col="blue")
  mtext(paste0("r = ", round(rlist[i],5)),cex=1.2)
}
par(op)
dev.off()
```

@@

if(noisetype=="extreme"){
  risk_left1<-Af$risk_xleft
  risk_right1<-Af$risk_xright

  risk_left2<-Al$risk_xleft
  risk_right2<-Al$risk_xright
}

if(noisetype=="moderate"){
  risk_left1<-Af$risk_mleft
  risk_right1<-Af$risk_mright

  risk_left2<-Al$risk_mleft
  risk_right2<-Al$risk_mright
}

>>>>

pdf("./Results/common_legend_extreme_and_moderate_noise.pdf",height=1,width=12)
op<-par(fig = c(0, 1, 0, 1), oma = c(0, 0, 0, 0), mar = c(0, 0, 0, 0))
plot(0, 0, type = "n", bty = "n", xaxt = "n", yaxt = "n")
legend("center", c("extreme LT","moderate LT", "moderate RT","extreme RT"), lty=c(1,1), pch=c(1,1,1,1), 
         col=c('red', 'orange','skyblue','blue'),x.intersp = 0.1,
         cex = 2.2, xpd = TRUE, horiz = T, inset = c(0,0), 
         bty = "n")
par(op)
dev.off()

@@

#----------------------- plot for extreme and moderate tail dep. noise ---------------------------------------
pdf(paste(resloc,"ricker_ext_risk_local_disp_extreme_and_moderate_noise.pdf",sep=""),height=9,width=9)
#op<-par(mfrow=c(3,3),mar=c(5.2,4.2,1.2,6.2))
op<-par(mfrow=c(3,3),mar=c(5,4,1.5,1.5),mgp=c(2,0.5,0))

  plot(ss$d,ss$risk_xleft,xlim=range(ss$d),ylim=c(0,1),type="b",col="red",
       #panel.first = grid(),
       xlab="d",ylab="Extinction risk",cex.lab=2,cex.axis=1.5)
  lines(ss$d,ss$risk_mleft,type="b",col="orange")
  lines(ss$d,ss$risk_mright,type="b",col="skyblue")
  lines(ss$d,ss$risk_xright,type="b",col="blue")
  #legend("bottomleft", c("noise : left","noise : right"), lty=c(1,1), pch=c(1,1), 
  #       col=c('red', 'blue'), horiz=T, bty='n', cex=1.2)
  mtext(paste0("r = ", round(rlist[i],5)),cex=1.2)

pdf(paste(resloc,"ricker_ext_risk_global_disp_extreme_and_moderate_noise.pdf",sep=""),height=9,width=9)
op<-par(mfrow=c(3,3),mar=c(5,4,1.5,1.5),mgp=c(2,0.5,0))

  plot(ss$d,ss$risk_xleft,xlim=range(ss$d),ylim=c(0,1),type="b",col="red",
       #panel.first = grid(),
       xlab="d",ylab="Extinction risk",cex.lab=2,cex.axis=1.5)
  lines(ss$d,ss$risk_mleft,type="b",col="orange")
  lines(ss$d,ss$risk_mright,type="b",col="skyblue")
  lines(ss$d,ss$risk_xright,type="b",col="blue")
  #legend("bottomleft", c("noise : left","noise : right"), lty=c(1,1), pch=c(1,1), 
  #       col=c('red', 'blue'), horiz=T, bty='n', cex=1.2)
  mtext(paste0("r = ", round(rlist[i],5)),cex=1.2)
}
par(op)
dev.off()
```

@@

lines(ricker_extrisk_d0$r,ricker_extrisk_d0$risk_mright_d0,col="blue",type="b",ylim=c(0,1),pch=1)
arrows(x0=ricker_extrisk_d0$r,y0=ricker_extrisk_d0$CI0.025mright,
       x1=ricker_extrisk_d0$r,y1=ricker_extrisk_d0$CI0.975mright,angle=90,length=0.1,col="blue",code=3)
legend("topleft", legend=c("Ricker"), horiz=F, bty='n',cex=1.8)  
mtext(paste0("K = ",K),side = 3, line=-16, adj=0.95, cex=1.8, col="black")
legend("bottomright",legend=bquote(sigma==.(scl)), horiz=F,bty='n',cex=1.8)
#legend("bottomright", legend=c("Ricker",paste0("K = ",K)), horiz=F, bty='n',cex=1.8)
par(op)
dev.off()

#-------------------- plot for extreme and moderate tail dep. noise ---------------------------------------
pdf(paste(resloc,"ricker_extrisk_d0_extreme_and_moderatenoise.pdf",sep=""),height=5,width=5)
op<-par(mar=c(5,4,1.5,1.5),mgp=c(2,0.7,0))

plot(ricker_extrisk_d0$r,ricker_extrisk_d0$risk_xleft_d0,col="red",type="b",
     ylim=c(0,1),xlim = range(ricker_extrisk_d0$r),xlab="r",ylab="Extinction risk",cex.lab=2,cex.axis=1.5,pch=1)
arrows(x0=ricker_extrisk_d0$r,y0=ricker_extrisk_d0$CI0.025xleft,x1=ricker_extrisk_d0$r,y1=ricker_extrisk_d0$CI0.975xleft,
       angle=90,length=0.1,col="red",code=3)
abline(v=rc_ricker,lty="dotted",col="black") #rc=1

lines(ricker_extrisk_d0$r,ricker_extrisk_d0$risk_mleft_d0,col="orange",type="b",ylim=c(0,1),pch=1)
arrows(x0=ricker_extrisk_d0$r,y0=ricker_extrisk_d0$CI0.025mleft,
       x1=ricker_extrisk_d0$r,y1=ricker_extrisk_d0$CI0.975mleft,angle=90,length=0.1,col="orange",code=3)

lines(ricker_extrisk_d0$r,ricker_extrisk_d0$risk_mright_d0,col="skyblue",type="b",ylim=c(0,1),pch=1)
arrows(x0=ricker_extrisk_d0$r,y0=ricker_extrisk_d0$CI0.025mright,
       x1=ricker_extrisk_d0$r,y1=ricker_extrisk_d0$CI0.975mright,angle=90,length=0.1,col="skyblue",code=3)

lines(ricker_extrisk_d0$r,ricker_extrisk_d0$risk_xright_d0,col="blue",type="b",ylim=c(0,1),pch=1)
arrows(x0=ricker_extrisk_d0$r,y0=ricker_extrisk_d0$CI0.025xright,
       x1=ricker_extrisk_d0$r,y1=ricker_extrisk_d0$CI0.975xright,angle=90,length=0.1,col="blue",code=3)

legend("topleft", legend=c("Ricker"), horiz=F, bty='n',cex=1.8)  
mtext(paste0("K = ",K),side = 3, line=-16, adj=0.95, cex=1.8, col="black")
legend("bottomright",legend=bquote(sigma==.(scl)), horiz=F,bty='n',cex=1.8)

@@

#----------------------- plot for extreme and moderate tail dep. noise ---------------------------------------
pdf(paste(resloc,"hassell_ext_risk_local_disp_extreme_and_moderate_noise.pdf",sep=""),height=12,width=12)
op<-par(mfrow=c(4,4),mar=c(5,4,1.5,1.5),mgp=c(2,0.5,0))

  plot(ss$d,ss$risk_xleft,xlim=range(ss$d),ylim=c(0,1),type="b",col="red",
       #panel.first = grid(),
       xlab="d",ylab="Extinction risk",cex.lab=2,cex.axis=1.5)
  lines(ss$d,ss$risk_mleft,type="b",col="orange")
  lines(ss$d,ss$risk_mright,type="b",col="skyblue")
  lines(ss$d,ss$risk_xright,type="b",col="blue")
  mtext(paste0("r = ", round(rlist[i],5)),cex=1.2)

pdf(paste(resloc,"hassell_ext_risk_global_disp_extreme_and_moderate_noise.pdf",sep=""),height=12,width=12)
op<-par(mfrow=c(4,4),mar=c(5,4,1.5,1.5),mgp=c(2,0.5,0))

  plot(ss$d,ss$risk_xleft,xlim=range(ss$d),ylim=c(0,1),type="b",col="red",
       #panel.first = grid(),
       xlab="d",ylab="Extinction risk",cex.lab=2,cex.axis=1.5)
  lines(ss$d,ss$risk_mleft,type="b",col="orange")
  lines(ss$d,ss$risk_mright,type="b",col="skyblue")
  lines(ss$d,ss$risk_xright,type="b",col="blue")
  mtext(paste0("r = ", round(rlist[i],5)),cex=1.2)
}
par(op)
dev.off()
```

@@

lines(hassell_extrisk_d0$r,hassell_extrisk_d0$risk_mright_d0,col="blue",type="b",ylim=c(0,1),pch=1)
arrows(x0=hassell_extrisk_d0$r,y0=hassell_extrisk_d0$CI0.025mright,
       x1=hassell_extrisk_d0$r,y1=hassell_extrisk_d0$CI0.975mright,angle=90,length=0.1,col="blue",code=3)
legend("topleft", legend=c("Hassell"), horiz=F, bty='n',cex=1.8)  
mtext(paste0("a = ",a,", b = ",b),side = 3, line=-16, adj=0.9, cex=1.8, col="black")
legend("bottomright",legend=bquote(sigma==.(scl)), horiz=F,bty='n',cex=1.8)
#legend("bottomright", c("Hassell",paste0("a = ",a," ,b = ",b),paste0("sd =",scl)), horiz=F, bty='n',cex=1.8)
par(op)
dev.off()

#-------------------- plot for extreme and moderate tail dep. noise ---------------------------------------
pdf(paste(resloc,"hassell_extrisk_d0_extreme_and_moderatenoise.pdf",sep=""),height=5,width=5)
op<-par(mar=c(5,4,1.5,1.5),mgp=c(2,0.7,0))

plot(hassell_extrisk_d0$r,hassell_extrisk_d0$risk_xleft_d0,col="red",type="b",ylim=c(0,1),xlim = range(hassell_extrisk_d0$r),
     xlab="r",ylab="Extinction risk",cex.lab=2,cex.axis=1.5,pch=1)
arrows(x0=hassell_extrisk_d0$r,y0=hassell_extrisk_d0$CI0.025xleft,
       x1=hassell_extrisk_d0$r,y1=hassell_extrisk_d0$CI0.975xleft,angle=90,length=0.1,col="red",code=3)
abline(v=rc_hassell,lty="dotted",col="black")

lines(hassell_extrisk_d0$r,hassell_extrisk_d0$risk_mleft_d0,col="orange",type="b",ylim=c(0,1),pch=1)
arrows(x0=hassell_extrisk_d0$r,y0=hassell_extrisk_d0$CI0.025mleft,
       x1=hassell_extrisk_d0$r,y1=hassell_extrisk_d0$CI0.975mleft,angle=90,length=0.1,col="orange",code=3)

lines(hassell_extrisk_d0$r,hassell_extrisk_d0$risk_mright_d0,col="skyblue",type="b",ylim=c(0,1),pch=1)
arrows(x0=hassell_extrisk_d0$r,y0=hassell_extrisk_d0$CI0.025mright,
       x1=hassell_extrisk_d0$r,y1=hassell_extrisk_d0$CI0.975mright,angle=90,length=0.1,col="skyblue",code=3)

lines(hassell_extrisk_d0$r,hassell_extrisk_d0$risk_xright_d0,col="blue",type="b",ylim=c(0,1),pch=1)
arrows(x0=hassell_extrisk_d0$r,y0=hassell_extrisk_d0$CI0.025xright,
       x1=hassell_extrisk_d0$r,y1=hassell_extrisk_d0$CI0.975xright,angle=90,length=0.1,col="blue",code=3)

legend("topleft", legend=c("Hassell"), horiz=F, bty='n',cex=1.8)  
mtext(paste0("a = ",a,", b = ",b),side = 3, line=-16, adj=0.9, cex=1.8, col="black")
legend("bottomright",legend=bquote(sigma==.(scl)), horiz=F,bty='n',cex=1.8)

@@

#---------------------- plot for extreme and moderate tail dep. noise ---------------------------------------
pdf(paste(resloc,"msmith_ext_risk_local_disp_extreme_and_moderatenoise.pdf",sep=""),height=12,width=12)
op<-par(mfrow=c(4,4),mar=c(5,4,1.5,1.5),mgp=c(2,0.5,0))

  plot(ss$d,ss$risk_mleft,xlim=range(ss$d),ylim=c(0,1),type="b",col="red",
       xlab="d",ylab="Extinction risk",cex.lab=2,cex.axis=1.5)
  lines(ss$d,ss$risk_mleft,type="b",col="orange")
  lines(ss$d,ss$risk_mright,type="b",col="skyblue")
  lines(ss$d,ss$risk_xright,type="b",col="blue")
  mtext(paste0("r = ", round(rlist[i],5)),cex=1.2)
}
par(op)
dev.off()

pdf(paste(resloc,"msmith_ext_risk_global_disp_extreme_and_moderatenoise.pdf",sep=""),height=12,width=12)
op<-par(mfrow=c(4,4),mar=c(5,4,1.5,1.5))

  plot(ss$d,ss$risk_mleft,xlim=range(ss$d),ylim=c(0,1),type="b",col="red",
       xlab="d",ylab="Extinction risk",cex.lab=2,cex.axis=1.5)
  lines(ss$d,ss$risk_mleft,type="b",col="orange")
  lines(ss$d,ss$risk_mright,type="b",col="skyblue")
  lines(ss$d,ss$risk_xright,type="b",col="blue")
  mtext(paste0("r = ", round(rlist[i],5)),cex=1.2)
}
par(op)
dev.off()
```

@@

lines(msmith_extrisk_d0$r,msmith_extrisk_d0$risk_mright_d0,col="blue",type="b",pch=1)
arrows(x0=msmith_extrisk_d0$r,y0=msmith_extrisk_d0$CI0.025mright,x1=msmith_extrisk_d0$r,
       y1=msmith_extrisk_d0$CI0.975mright,angle=90,length=0.1,col="blue",code=3)
legend("topleft", legend=c("Maynard Smith"), horiz=F, bty='n',cex=1.8)  
mtext(paste0("a = ",a,", b = ",b),side = 3, line=-16, adj=0.9, cex=1.8, col="black")
legend("bottomright",legend=bquote(sigma==.(scl)), horiz=F,bty='n',cex=1.8)
par(op)
dev.off()

#-------------------- plot for extreme and moderate tail dep. noise ---------------------------------------
pdf(paste(resloc,"msmith_extrisk_d0_extreme_and_moderatenoise.pdf",sep=""),height=5,width=5)
op<-par(mar=c(5,4,1.5,1.5),mgp=c(2,0.7,0))

plot(msmith_extrisk_d0$r,msmith_extrisk_d0$risk_xleft_d0,col="red",type="b",ylim=c(0,1),xlim = range(msmith_extrisk_d0$r),
     xlab="r",ylab="Extinction risk",cex.lab=2,cex.axis=1.5,pch=1)
arrows(x0=msmith_extrisk_d0$r,y0=msmith_extrisk_d0$CI0.025xleft,
       x1=msmith_extrisk_d0$r,y1=msmith_extrisk_d0$CI0.975xleft,angle=90,length=0.1,col="red",code=3)
abline(v=rc_msmith,lty="dotted",col="black")

lines(msmith_extrisk_d0$r,msmith_extrisk_d0$risk_mleft_d0,col="orange",type="b",ylim=c(0,1),pch=1)
arrows(x0=msmith_extrisk_d0$r,y0=msmith_extrisk_d0$CI0.025mleft,
       x1=msmith_extrisk_d0$r,y1=msmith_extrisk_d0$CI0.975mleft,angle=90,length=0.1,col="orange",code=3)

lines(msmith_extrisk_d0$r,msmith_extrisk_d0$risk_mright_d0,col="skyblue",type="b",ylim=c(0,1),pch=1)
arrows(x0=msmith_extrisk_d0$r,y0=msmith_extrisk_d0$CI0.025mright,
       x1=msmith_extrisk_d0$r,y1=msmith_extrisk_d0$CI0.975mright,angle=90,length=0.1,col="skyblue",code=3)

lines(msmith_extrisk_d0$r,msmith_extrisk_d0$risk_xright_d0,col="blue",type="b",ylim=c(0,1),pch=1)
arrows(x0=msmith_extrisk_d0$r,y0=msmith_extrisk_d0$CI0.025xright,
       x1=msmith_extrisk_d0$r,y1=msmith_extrisk_d0$CI0.975xright,angle=90,length=0.1,col="blue",code=3)

legend("topleft", legend=c("Maynard Smith"), horiz=F, bty='n',cex=1.8)  
mtext(paste0("a = ",a,", b = ",b),side = 3, line=-16, adj=0.9, cex=1.8, col="black")
legend("bottomright",legend=bquote(sigma==.(scl)), horiz=F,bty='n',cex=1.8)

@@

#--------------------------- plot for extreme and moderate tail dep. noise ---------------------------------------
pdf(paste(resloc,"pennycuick_ext_risk_local_disp_extreme_and_moderatenoise.pdf",sep=""),height=12,width=12)
op<-par(mfrow=c(4,4),mar=c(5,4,1.2,1.5),mgp=c(2,0.5,0))

  plot(ss$d,ss$risk_mleft,xlim=range(ss$d),ylim=c(0,1),type="b",col="red",
       xlab="d",ylab="Extinction risk",cex.lab=2,cex.axis=1.5)
  lines(ss$d,ss$risk_mleft,type="b",col="orange")
  lines(ss$d,ss$risk_mright,type="b",col="skyblue")
  lines(ss$d,ss$risk_xright,type="b",col="blue")
  mtext(paste0("r = ", round(rlist[i],5)),cex=1.2)
}
par(op)
dev.off()

pdf(paste(resloc,"pennycuick_ext_risk_global_disp_extreme_and_moderatenoise.pdf",sep=""),height=12,width=12)
op<-par(mfrow=c(4,4),mar=c(5,4,1.5,1.5),mgp=c(2,0.5,0))

  plot(ss$d,ss$risk_mleft,xlim=range(ss$d),ylim=c(0,1),type="b",col="red",
       xlab="d",ylab="Extinction risk",cex.lab=2,cex.axis=1.5)
  lines(ss$d,ss$risk_mleft,type="b",col="orange")
  lines(ss$d,ss$risk_mright,type="b",col="skyblue")
  lines(ss$d,ss$risk_xright,type="b",col="blue")
  mtext(paste0("r = ", round(rlist[i],5)),cex=1.2)
}
par(op)
dev.off()
```

@@

lines(pennycuick_extrisk_d0$r,pennycuick_extrisk_d0$risk_mright_d0,col="blue",type="b",ylim=c(0,1),pch=1)
arrows(x0=pennycuick_extrisk_d0$r,y0=pennycuick_extrisk_d0$CI0.025mright,x1=pennycuick_extrisk_d0$r,
       y1=pennycuick_extrisk_d0$CI0.975mright,angle=90,length=0.1,col="blue",code=3)
legend("topleft", legend=c("Pennycuick"), horiz=F, bty='n',cex=1.8)  
mtext(paste0("a = ",a,", b = ",b),side = 3, line=-16, adj=0.9, cex=1.8, col="black")
legend("bottomright",legend=bquote(sigma==.(scl)), horiz=F,bty='n',cex=1.8)
#legend("bottomright", c("Pennycuick",paste0("a = ",a," ,b = ",b),paste0("sd =",scl)), horiz=F, bty='n',cex=1.8)
par(op)
dev.off()

#-------------------- plot for extreme and moderate tail dep. noise ---------------------------------------
pdf(paste(resloc,"pennycuick_extrisk_d0_extreme_and_moderatenoise.pdf",sep=""),height=5,width=5)
op<-par(mar=c(5,4,1.5,1.5),mgp=c(2,0.7,0))

plot(pennycuick_extrisk_d0$r,pennycuick_extrisk_d0$risk_xleft_d0,col="red",type="b",ylim=c(0,1),xlim = range(pennycuick_extrisk_d0$r),
     xlab="r",ylab="Extinction risk",cex.lab=2,cex.axis=1.5,pch=1)
arrows(x0=pennycuick_extrisk_d0$r,y0=pennycuick_extrisk_d0$CI0.025xleft,
       x1=pennycuick_extrisk_d0$r,y1=pennycuick_extrisk_d0$CI0.975xleft,angle=90,length=0.1,col="red",code=3)
abline(v=rc_pennycuick,lty="dotted",col="black")

lines(pennycuick_extrisk_d0$r,pennycuick_extrisk_d0$risk_mleft_d0,col="orange",type="b",ylim=c(0,1),pch=1)
arrows(x0=pennycuick_extrisk_d0$r,y0=pennycuick_extrisk_d0$CI0.025mleft,
       x1=pennycuick_extrisk_d0$r,y1=pennycuick_extrisk_d0$CI0.975mleft,angle=90,length=0.1,col="orange",code=3)

lines(pennycuick_extrisk_d0$r,pennycuick_extrisk_d0$risk_mright_d0,col="skyblue",type="b",ylim=c(0,1),pch=1)
arrows(x0=pennycuick_extrisk_d0$r,y0=pennycuick_extrisk_d0$CI0.025mright,
       x1=pennycuick_extrisk_d0$r,y1=pennycuick_extrisk_d0$CI0.975mright,angle=90,length=0.1,col="skyblue",code=3)

lines(pennycuick_extrisk_d0$r,pennycuick_extrisk_d0$risk_xright_d0,col="blue",type="b",ylim=c(0,1),pch=1)
arrows(x0=pennycuick_extrisk_d0$r,y0=pennycuick_extrisk_d0$CI0.025xright,
       x1=pennycuick_extrisk_d0$r,y1=pennycuick_extrisk_d0$CI0.975xright,angle=90,length=0.1,col="blue",code=3)

legend("topleft", legend=c("Pennycuick"), horiz=F, bty='n',cex=1.8)  
mtext(paste0("a = ",a,", b = ",b),side = 3, line=-16, adj=0.9, cex=1.8, col="black")
legend("bottomright",legend=bquote(sigma==.(scl)), horiz=F,bty='n',cex=1.8)

@@

#------------------------- plot for extreme and moderate tail dep. noise ---------------------------------------
pdf(paste(resloc,"verhulst_ext_risk_local_disp_extreme_and_moderatenoise.pdf",sep=""),height=9,width=9)
op<-par(mfrow=c(3,3),mar=c(5,4,1.5,1.5),mgp=c(2,0.5,0))

  plot(ss$d,ss$risk_mleft,xlim=range(ss$d),ylim=c(0,1),type="b",col="red",
       xlab="d",ylab="Extinction risk",cex.lab=2,cex.axis=1.5)
  lines(ss$d,ss$risk_mleft,type="b",col="orange")
  lines(ss$d,ss$risk_mright,type="b",col="skyblue")
  lines(ss$d,ss$risk_xright,type="b",col="blue")
  mtext(paste0("r = ", round(rlist[i],5)),cex=1.2)
}
par(op)
dev.off()

pdf(paste(resloc,"verhulst_ext_risk_global_disp_extreme_and_moderatenoise.pdf",sep=""),height=9,width=9)
op<-par(mfrow=c(3,3),mar=c(5,4,1.5,1.5),mgp=c(2,0.5,0))

  plot(ss$d,ss$risk_mleft,xlim=range(ss$d),ylim=c(0,1),type="b",col="red",
       xlab="d",ylab="Extinction risk",cex.lab=2,cex.axis=1.5)
  lines(ss$d,ss$risk_mleft,type="b",col="orange")
  lines(ss$d,ss$risk_mright,type="b",col="skyblue")
  lines(ss$d,ss$risk_xright,type="b",col="blue")
  mtext(paste0("r = ", round(rlist[i],5)),cex=1.2)
}
par(op)
dev.off()
```

@@

lines(verhulst_extrisk_d0$r,verhulst_extrisk_d0$risk_mright_d0,col="blue",type="b",pch=1)
arrows(x0=verhulst_extrisk_d0$r,y0=verhulst_extrisk_d0$CI0.025mright,
       x1=verhulst_extrisk_d0$r,y1=verhulst_extrisk_d0$CI0.975mright,angle=90,length=0.1,col="blue",code=3)
legend("topleft", legend=c("Verhulst"), horiz=F, bty='n',cex=1.8)  
mtext(paste0("K = ",K),side = 3, line=-16, adj=0.9, cex=1.8, col="black")
legend("bottomright",legend=bquote(sigma==.(scl)), horiz=F,bty='n',cex=1.8)
#legend("bottomright", c("Verhulst",paste0("K =1, sd =",scl)), horiz=F, bty='n',cex=1.8)
par(op)
dev.off()

#-------------------- plot for extreme and moderate tail dep. noise ---------------------------------------
pdf(paste(resloc,"verhulst_extrisk_d0_extreme_and_moderatenoise.pdf",sep=""),height=5,width=5)
op<-par(mar=c(5,4,1.5,1.5),mgp=c(2,0.7,0))

plot(verhulst_extrisk_d0$r,verhulst_extrisk_d0$risk_xleft_d0,col="red",type="b",ylim=c(0,1),xlim = range(verhulst_extrisk_d0$r),
     xlab="r",ylab="Extinction risk",cex.lab=2,cex.axis=1.5,pch=1)
arrows(x0=verhulst_extrisk_d0$r,y0=verhulst_extrisk_d0$CI0.025xleft,
       x1=verhulst_extrisk_d0$r,y1=verhulst_extrisk_d0$CI0.975xleft,angle=90,length=0.1,col="red",code=3)
abline(v=rc_verhulst,lty="dotted",col="black")

lines(verhulst_extrisk_d0$r,verhulst_extrisk_d0$risk_mleft_d0,col="orange",type="b",ylim=c(0,1),pch=1)
arrows(x0=verhulst_extrisk_d0$r,y0=verhulst_extrisk_d0$CI0.025mleft,
       x1=verhulst_extrisk_d0$r,y1=verhulst_extrisk_d0$CI0.975mleft,angle=90,length=0.1,col="orange",code=3)

lines(verhulst_extrisk_d0$r,verhulst_extrisk_d0$risk_mright_d0,col="skyblue",type="b",ylim=c(0,1),pch=1)
arrows(x0=verhulst_extrisk_d0$r,y0=verhulst_extrisk_d0$CI0.025mright,
       x1=verhulst_extrisk_d0$r,y1=verhulst_extrisk_d0$CI0.975mright,angle=90,length=0.1,col="skyblue",code=3)

lines(verhulst_extrisk_d0$r,verhulst_extrisk_d0$risk_xright_d0,col="blue",type="b",ylim=c(0,1),pch=1)
arrows(x0=verhulst_extrisk_d0$r,y0=verhulst_extrisk_d0$CI0.025xright,
       x1=verhulst_extrisk_d0$r,y1=verhulst_extrisk_d0$CI0.975xright,angle=90,length=0.1,col="blue",code=3)

legend("topleft", legend=c("Verhulst"), horiz=F, bty='n',cex=1.8)  
mtext(paste0("K = ",K),side = 3, line=-16, adj=0.9, cex=1.8, col="black")
legend("bottomright",legend=bquote(sigma==.(scl)), horiz=F,bty='n',cex=1.8)

@@

#--------------------- plot for extreme and moderate tail dep. noise ---------------------------------------
pdf(paste(resloc,"abrewer_ext_risk_local_disp_extreme_and_moderatenoise.pdf",sep=""),height=9,width=9)
op<-par(mfrow=c(3,3),mar=c(5,4,1.5,1.5),mgp=c(2,0.5,0))

  plot(ss$d,ss$risk_mleft,xlim=range(ss$d),ylim=c(0,1),type="b",col="red",
       xlab="d",ylab="Extinction risk",cex.lab=2,cex.axis=1.5)
  lines(ss$d,ss$risk_mleft,type="b",col="orange")
  lines(ss$d,ss$risk_mright,type="b",col="skyblue")
  lines(ss$d,ss$risk_xright,type="b",col="blue")
  mtext(paste0("r = ", round(rlist[i],5)),cex=1.2)
}
par(op)
dev.off()

pdf(paste(resloc,"abrewer_ext_risk_global_disp_extreme_and_moderatenoise.pdf",sep=""),height=9,width=9)
op<-par(mfrow=c(3,3),mar=c(5,4,1.5,1.5),mgp=c(2,0.5,0))

  plot(ss$d,ss$risk_mleft,xlim=range(ss$d),ylim=c(0,1),type="b",col="red",
       xlab="d",ylab="Extinction risk",cex.lab=2,cex.axis=1.5)
  lines(ss$d,ss$risk_mleft,type="b",col="orange")
  lines(ss$d,ss$risk_mright,type="b",col="skyblue")
  lines(ss$d,ss$risk_xright,type="b",col="blue")
  mtext(paste0("r = ", round(rlist[i],5)),cex=1.2)
}
par(op)
dev.off()
```

@@

if(noisetype=="both"){
   plot(Af$d,Af$risk_xleft,xlim=range(Af$d),ylim=c(0,1),type="b",col="red",
     xlab="d",ylab="Extinction risk",cex.lab=1.5,cex.axis=1.5)
   lines(Af$d,Af$risk_mleft,type="b",col="orange")
   lines(Af$d,Af$risk_mright,type="b",col="skyblue")
   lines(Af$d,Af$risk_xright,type="b",col="blue")
